A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 4_method.tex
reconceptualize rounding as flattening

\section{Method}
\subsection{Overview}
The naive method consists of consecutive inward offsets from the outline using a constant bead width.
These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones of \SI{45}{\degree} which are touching the input shape. \cite{blum1967transformation}
The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
We can therefore use the MAT to efficiently calculate the consecutive offsets defining the naive toolpathing. \cite{eiamsa2003toward}

For the naive method the overfill and underfill problems arise in the center,
because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
We therefore change the UoC mesh such that an exact integer beads will be generated in the center.
More specifically, we round the height to the nearest multiple of \emph{half} the nozzle size.
That way we allow for an odd number of beads to be placed between the two sides of the outline shape.

Our technique consists of the folowing steps:
\begin{itemize}
\item Compute the mesh representing the Union of Cones (UoC) for the input shape
\item Identify central regions of the UoC
\item Round the heights of central nodes to to the nearest slicing height
\item Smooth out sharp transitions between regions with different integer heights
\item Determine the heights in the periphery (non-central regions)
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Rounded}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and round the height values to the nearest integer muliple of half the nozzle width \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Rounding the heights in the central mesh regions and smoothing those heights is handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/skeleton.pdf}
\caption{Skeleton}\label{overview_fig_skeleton}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/marked.pdf}
\caption{Marked}\label{overview_fig_marked}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/transitions.pdf}
\caption{Transitions}\label{overview_fig_transitions}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/junctions.png}
\caption{Junctions}\label{overview_fig_junctions}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/toolpaths.png}
\caption{Toolpaths}\label{overview_fig_toolpaths}
\end{subfigure}
\caption{
Overview of the steps in the method of our framework.
First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine an initial bead count (numbers) based on the local feature size.
Then we \subref{overview_fig_transitions} make alterations to smoothly transition to a different bead count (magenta).
We then \subref{overview_fig_junctions} generate a number of junctions (yellow) equal to the bead count along the bones of the skeleton,
which are \subref{overview_fig_toolpaths} connected together to make the toolpaths.
}
\label{overview_fig}
\end{figure*}

@@

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we can round the heights to integer multiples of half the nozzle size.
We assign each node a new height value measured in terms of an integer number: it's \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.

\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $b(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framewotk the function $b$ is determined by a beading strategy.

We first assign each marked node $v$ of the skeleton an initial bead count $b^*_v \leftarrow b(2R(v))$.
We then filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Initial bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition remp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

\subsubsection{Transitioning}
For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the preferred bead count $b(2R(v))$ changes.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $b^{-1}(n) := \argmax_d b(d) = n$.
%For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ b^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

@@

\subsubsection{Height smoothing}
In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e. where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
See \cref{transitions}.
The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.

>>>>

\section{Method}
\subsection{Overview}
The naive method consists of consecutive inward offsets from the outline using a constant bead width.
These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape. \cite{blum1967transformation}
The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
We can therefore use the MAT to efficiently calculate the consecutive offsets defining the naive toolpathing. \cite{eiamsa2003toward}

For the naive method the overfill and underfill problems arise in the center,
because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.

Our framework can be thought of as following these steps:
\begin{itemize}
\item Compute the skeleton of the input shape
\item Assign each node a height in terms of bead count based on the local feature size
\item Identify central regions of the UoC
\item Flatten the central regions at heights equal to the nearest integer bead count
\item Smooth out sharp transitions between regions with different integer heights
\item Determine the heights in the periphery (non-central regions)
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Flattened}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and flatten those regions to heights of the nearest integer \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Flattening the central mesh regions and smoothing are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/skeleton.pdf}
\caption{Skeleton}\label{overview_fig_skeleton}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/marked.pdf}
\caption{Marked}\label{overview_fig_marked}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/transitions.pdf}
\caption{Transitions}\label{overview_fig_transitions}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/junctions.png}
\caption{Junctions}\label{overview_fig_junctions}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/toolpaths.png}
\caption{Toolpaths}\label{overview_fig_toolpaths}
\end{subfigure}
\caption{
Overview of the steps in the method of our framework.
First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine a bead count (numbers) based on the local feature size.
Then we \subref{overview_fig_transitions} make alterations to smoothly transition to a different bead count (magenta).
We then \subref{overview_fig_junctions} generate a number of junctions (yellow) equal to the bead count along the bones of the skeleton,
which are \subref{overview_fig_toolpaths} connected together to make the toolpaths.
}
\label{overview_fig}
\end{figure*}

@@

\subsubsection{Union of cones}
In order to transform the ST into a 3D surface we add another dimension to the skeleton.
We assign each node a new height value measured in terms of an integer number: it's \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.

For each node $v$ we assign an initial bead count based on the feature diameter $2R$ and the nozzle size $w_\text{pref}$: $b^*_v \leftarrow 2 R(v) / w_\text{pref}$.
The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method was described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we flatten those regions to integer heights.
More specifically we round the heights to integer bead count values.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a flattening operator which maps a feature diameter to a bead count: $f: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framewotk the function $b$ is determined by a beading strategy.

We first assign each marked node $v$ of the skeleton the bead count $b^*_v \leftarrow f(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

\subsubsection{Flattening}
For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
%For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ f^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

@@

\subsubsection{Smoothing}
In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e. where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
See \cref{transitions}.
The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.

### 2019-08-23 5_generalization.tex
reconceptualize rounding as flattening

\begin{definition}\label{beading_strategy_definition}
We define a beading strategy as the following set:
$$
\left\{ \alpha_\text{max}, b(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
$$
where
$\alpha_{\text{max}}$ (the limit bisector angle),
$b(d)$ (optimal bead count),
$t(n)$ (transition length)
and
$t_0(n)$ (transition anchor position) have already been defined above.
We introduce here
$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
and
$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
\end{enumerate}

@@

A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( b^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\paragraph{Naive Beading Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
t(n) &= 0 \\
b(d) &=
\begin{cases}
1 & \text{ if } d < w_\text{pref} \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_\text{pref} & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_\text{pref} / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\begin{align*}
\alpha_\text{max} &= \SI{0}{\degree} \\
b(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $b^(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

\begin{align*}
t(n) &= \frac12 w_\text{pref} \\
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
b(d) &= b^-(d) +
\begin{cases}
-1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

\begin{align*}
b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
E(n,d) &= d - n w_\text{pref} \\
W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

>>>>

\begin{definition}\label{beading_strategy_definition}
We define a beading strategy as the following set:
$$
\left\{ \alpha_\text{max}, f(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
$$
where
$\alpha_{\text{max}}$ (the limit bisector angle),
$f(d)$ (flattening operator),
$t(n)$ (transition length)
and
$t_0(n)$ (transition anchor position) have already been defined above.
We introduce here
$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
and
$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ f^{-1}(n + 1) - f^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
\end{enumerate}

@@

A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( f^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\paragraph{Naive Beading Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
t(n) &= 0 \\
f(d) &=
\begin{cases}
1 & \text{ if } d < w_\text{pref} \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_\text{pref} & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_\text{pref} / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\begin{align*}
\alpha_\text{max} &= \SI{0}{\degree} \\
f(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $f^-(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

\begin{align*}
t(n) &= \frac12 w_\text{pref} \\
f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
f(d) &= f^-(d) +
\begin{cases}
-1 & \text{ if } f^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  f^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

\begin{align*}
f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
E(n,d) &= d - n w_\text{pref} \\
W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}
